\part*{Task 1: Choosing a Mobile App}
\addcontentsline{toc}{part}{Task 1: Choosing a Mobile App}

Loneliness in aging populations is an important issue, especially in Canada.

\section*{Introduction and Background}
\addcontentsline{toc}{section}{Introduction and Background}

The well-being of the elderly population is strongly correlated to the quality
    of their social lives.
Loneliness substantially increases the risk of depression, mood disorders, and
    feelings of hopelessness in the elderly \cite{golden}.
This problem is especially daunting in Canada, where, according to estimates by
    the Government of Canada, 40\% of Canadian adults will be seniors by 2038
    \cite{canada}.

Many apps exist that aim to fulfill the need of maintaining social connections
    and staying in contact with friends and family.
Out of these apps and services, GrandPad stands out in its ability to meet user
    needs.

\section*{GrandPad}
\addcontentsline{toc}{section}{GrandPad}

GrandPad
    (Google Play ID
    \href
        {https://play.google.com/store/apps/details?id=net.grandpad.puma&hl=en}
        {net.grandpad.puma})
    is an app used to maintain a private social network between loved ones,
    including a senior user who owns a GrandPad tablet.

The app's goals are to provide instant messaging and high-quality video-calling
    in real-time across the world with secure connections.
As a simple, no-frills service to stay connected with loved ones, WhatsApp
    Messenger provides an easy-to-use app that can be utilized to maintain
    social connections across geographical barriers.

GrandPad's goal is to provide a platform for maintaining the social network of a
    senior loved one.
The app, along with the GrandPad tablet for elderly users, provides a
    user-friendly interface for audio and video calls, messages, sharing of
    photos and videos, and online games.
As a simple, no-frills service to keep a network of family members and friends
    connected, GrandPad provides an easy-to-use app that can be utilized to
    maintain social connections across geographical barriers.

Research conducted on this topic found that the majority of GrandPad users found
    the platform easy to use and felt more connected from using it
    \cite{grandpad_feasability}.
GrandPad is especially promising when compared with modern social media services,
    whose newsfeed-style platforms have mixed results in fostering meaningful
    socialization \cite{longjing}.
Currently, GrandPad stands out to be a leading tool in the category of senior
    apps for maintaining social connections.
